A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
5d refs
BRST

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[1]$.
\item Matter bosons $\nu\in\Omega^{0,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U)[-1]$, $\varphi \in \Omega^{2,0} (M ; U)[1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U)[1]$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

\begin{thm}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{thm}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}

>>>>

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[4n-2]$ and $a \in\Omega^{0}(M; \gg)[-4n+2]$;
\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[4n-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-4n+1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[1]$.
\item Matter bosons $\nu\in\Omega^{0,0}(M; U)[-2n]$, $\phi\in\Omega^0(M; U)[2n]$.
\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U)[2n-1]$, $\varphi \in \Omega^{2,0} (M ; U)[-2n+1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U)[-2n+1]$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

\begin{theorem}
The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\label{thm:4dholomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varphi . \\
\end{align*}
